---
title: "Filtering of POIs"
author: "Charles Alba"
date: "January 30, 2021"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Install the neccessary Packages

```{r}
require(sp)  
require(rgdal)
require(maps)
args = commandArgs(trailingOnly=TRUE)
```

# Read and filter poi dataset part 1 based on National park geometry 
part 1.  

```{r}

org_data<-read.csv("core_poi-part1.csv")
org_data<-subset(org_data,!is.na(org_data$latitude))
org_data<-subset(org_data,!is.na(org_data$longitude))
org_data$row_number<-rownames(org_data)
data<-read.csv("core_poi-part1.csv")
data<-subset(data,!is.na(data$latitude))
data<-subset(data,!is.na(data$longitude))
data$row_number<-rownames(data)
coordinates(data)<-c("longitude","latitude")
poly <- readOGR("National_Parks","National_Parks")


poly_wgs84 <- spTransform(poly, CRS("+proj=longlat +datum=WGS84"))
proj4string(data)<-proj4string(poly_wgs84)
plot(poly_wgs84)
plot(data, add=TRUE, col="red")
poly_ID<-over(data, poly_wgs84)
poly_ID<-poly_ID[!is.na(poly_ID$OBJECTID), ]
poly_ID$row_number<-rownames(poly_ID)
newData <- merge(poly_ID, org_data, by.x="row_number", by.y="row_number", all.x=T)
```

# Read and filter poi dataset part 2 based on National park geometry 
part 2.  

```{r}
org_data2<-read.csv("core_poi-part2.csv")
org_data2<-subset(org_data2,!is.na(org_data2$latitude))
org_data2<-subset(org_data2,!is.na(org_data2$longitude))
org_data2$row_number<-rownames(org_data2)
data2<-read.csv("core_poi-part2.csv")
data2<-subset(data2,!is.na(data2$latitude))
data2<-subset(data2,!is.na(data2$longitude))
data2$row_number<-rownames(data2)
coordinates(data2)<-c("longitude","latitude")
poly2 <- readOGR("National_Parks","National_Parks")


poly_wgs84_2 <- spTransform(poly2, CRS("+proj=longlat +datum=WGS84"))
proj4string(data2)<-proj4string(poly_wgs84_2)
#plot(poly_wgs84)
#plot(data, add=TRUE, col="red")
poly_ID2<-over(data2, poly_wgs84_2)
poly_ID2<-poly_ID2[!is.na(poly_ID2$OBJECTID), ]
poly_ID2$row_number<-rownames(poly_ID2)
newData2 <- merge(poly_ID2, org_data2, by.x="row_number", by.y="row_number", all.x=T)

```
# Read and filter poi dataset part 3 based on National park geometry 
part 3.  

```{r}
org_data3<-read.csv("core_poi-part3.csv")
org_data3<-subset(org_data3,!is.na(org_data3$latitude))
org_data3<-subset(org_data3,!is.na(org_data3$longitude))
org_data3$row_number<-rownames(org_data3)
data3<-read.csv("core_poi-part3.csv")
data3<-subset(data3,!is.na(data3$latitude))
data3<-subset(data3,!is.na(data3$longitude))
data3$row_number<-rownames(data3)
coordinates(data3)<-c("longitude","latitude")
poly3 <- readOGR("National_Parks","National_Parks")


poly_wgs84_3 <- spTransform(poly3, CRS("+proj=longlat +datum=WGS84"))
proj4string(data3)<-proj4string(poly_wgs84_3)
#plot(poly_wgs84)
#plot(data, add=TRUE, col="red")
poly_ID3<-over(data3, poly_wgs84_3)
poly_ID3<-poly_ID3[!is.na(poly_ID3$OBJECTID), ]
poly_ID3$row_number<-rownames(poly_ID3)
newData3 <- merge(poly_ID3, org_data3, by.x="row_number", by.y="row_number", all.x=T)

```
# Read and filter poi dataset part 4 based on National park geometry 
part 4.


```{r}
org_data4<-read.csv("core_poi-part4.csv")
org_data4<-subset(org_data4,!is.na(org_data4$latitude))
org_data4<-subset(org_data4,!is.na(org_data4$longitude))
org_data4$row_number<-rownames(org_data4)
data4<-read.csv("core_poi-part4.csv")
data4<-subset(data4,!is.na(data4$latitude))
data4<-subset(data4,!is.na(data4$longitude))
data4$row_number<-rownames(data4)
coordinates(data4)<-c("longitude","latitude")
poly4 <- readOGR("National_Parks","National_Parks")


poly_wgs84_4 <- spTransform(poly4, CRS("+proj=longlat +datum=WGS84"))
proj4string(data4)<-proj4string(poly_wgs84_4)
#plot(poly_wgs84)
#plot(data, add=TRUE, col="red")
poly_ID4<-over(data4, poly_wgs84_4)
poly_ID4<-poly_ID4[!is.na(poly_ID4$OBJECTID), ]
poly_ID4$row_number<-rownames(poly_ID4)
newData4 <- merge(poly_ID4, org_data4, by.x="row_number", by.y="row_number", all.x=T)

```

# Read and filter poi dataset part 5 based on National park geometry 
part 5.  

```{r}
org_data5<-read.csv("core_poi-part5.csv")
org_data5<-subset(org_data5,!is.na(org_data5$latitude))
org_data5<-subset(org_data5,!is.na(org_data5$longitude))
org_data5$row_number<-rownames(org_data5)
data5<-read.csv("core_poi-part5.csv")
data5<-subset(data5,!is.na(data5$latitude))
data5<-subset(data5,!is.na(data5$longitude))
data5$row_number<-rownames(data5)
coordinates(data5)<-c("longitude","latitude")
poly5 <- readOGR("National_Parks","National_Parks")


poly_wgs84_5 <- spTransform(poly5, CRS("+proj=longlat +datum=WGS84"))
proj4string(data5)<-proj4string(poly_wgs84_5)
#plot(poly_wgs84)
#plot(data, add=TRUE, col="red")
poly_ID5<-over(data5, poly_wgs84_5)
poly_ID5<-poly_ID5[!is.na(poly_ID5$OBJECTID), ]
poly_ID5$row_number<-rownames(poly_ID5)
newData5 <- merge(poly_ID5, org_data5, by.x="row_number", by.y="row_number", all.x=T)

```
# because "North Cascades National Park" has inaccurate coordinates on SafeGraph's POI database, we have manually extract this POI
```{r}
safegraph<-rbind(org_data,org_data2,org_data3,org_data4,org_data5)
safegraph_special_extraction<-safegraph[(safegraph$safegraph_place_id == "sg:a8c7746858474c499a242705615235b2"),]

```

# Concatenate data  

Concatenate the 5 datasets  (newData)

```{r}
filtered_pois <- rbind(newData, newData2, newData3, newData4, newData5)
filtered_pois<- rbind(filtered_pois, safegraph_special_extraction)
```

# Write data  

```{r}
filtered_pois = subset(filtered_pois, select = -c(row_number))
filtered_pois<-data.table(filtered_pois)
write.csv(filtered_pois,'national_park_visitation_analysis_w_mobile_phone_data/volume/data/interim/filtered_pois/filtered_POIs_based_on_geometry/filtered_pois.csv')
```

# further filtering for simplicity purposes  


```{r}
filtered_pois = subset(filtered_pois, select = c(UNIT_NAME,UNIT_TYPE,PARKNAME,pPolyID,placekey,safegraph_place_id, parent_placekey,parent_safegraph_place_id,location_name,safegraph_brand_ids,brands,top_category,sub_category,naics_code,latitude,longitude))


filtered_pois<-data.table(filtered_pois)
write.csv(filtered_pois,'national_park_visitation_analysis_w_mobile_phone_data/volume/data/interim/filtered_pois/filtered_POIs_based_on_geometry/small_filtered_pois.csv')
```
