# Reading the data and preparing it for the regression analysis. 
## Download library packages and load datasets
```{r}
library(effects)
library(cowplot)
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
library(ggpubr)
library(effects)
library(stargazer)
library(purrr)
library(plm)
library(data.table)
library(bit64)
options(scipen = 999)
library(knitr)
library(broom)
library(tseries) # for `adf.test()`
library(dynlm) #for function `dynlm()`
library(vars) # for function `VAR()`
library(nlWaldTest) # for the `nlWaldtest()` function
library(lmtest) #for `coeftest()` and `bptest()`.
library(car) #for `hccm()` robust standard errors
library(sandwich)
library(knitr) #for `kable()`
library(forecast) 
library(systemfit)
library(AER)
library(xtable)
library(jtools)
library(devtools)
library(interactions)
library(ggplot2)
library(sjPlot)
library(sjmisc)
data<-read.csv("national_park_visitation_analysis_w_mobile_phone_data/volume/data/processed/processed_model.csv")
data<-subset(data, select = c(vistor_census_block,minorityportion,median.age,dist,MEDIAN.INCOME, visitor_count, PARKNAME, date_range_start))
data<-data[complete.cases(data), ]
data$dist<-(data$dist)/1000 # Standardize distance to kilometers
```

## Remove Puerto Rico, Hawaii, Alaska, US minor Islands. 
```{r}
data$length<-floor(log10(data$vistor_census_block)) + 1
data_eleven<-data[(data$length==11),]
data_eleven$first<-as.numeric(substr(data_eleven$vistor_census_block, 1, 1))
data_twelve<-data[(data$length==12),]
data_twelve$first_second<-as.numeric(substr(data_twelve$vistor_census_block, 1, 2))
data_eleven<-data_eleven[!data_eleven$first == 2, ]
cbg_unwanted<-c(60,66,69,72,78,15)
data_twelve<-data_twelve[!data_twelve$first_second %in% cbg_unwanted,]
data_eleven<-subset(data_eleven, select=-c(length, first))
data_twelve<-subset(data_twelve, select=-c(length, first_second))
data<-rbind(data_eleven,data_twelve)
```
# Getting summary Statistics
```{r}
data_race<-subset(data,select=c(vistor_census_block,population_per_thousand,percent_black,percent_hispanic,percent_asian,percent_indian,minorityportion))
data_race<-data_race[!duplicated(data_race), ]
data_race<-data_race[complete.cases(data_race), ]
```

```{r}
summary(data_race)
```

```{r}
nrow(data_race)
```
```{r}
summary(data)
```

```{r}
nrow(data)
```


## Prepare the model for Regression. 
```{r}
data[data==0] = 0.0000000000000000000001 # Beacause natural log could not take 0's
# Classify COVID vs non-COVID era
data$date_range_start<-as.Date(data$date_range_start,"%Y-%m-%d") 
data_non<-data[(data$date_range_start<"2020-03-01"),]
data_covid<-data[(data$date_range_start>="2020-03-01"),]
data_covid$covid_era<-TRUE
data_non$covid_era<-FALSE
data<-rbind(data_covid, data_non)
data<-data[complete.cases(data), ]
data$date_range_start<-month(as.POSIXlt(data$date_range_start, format="%d/%m/%Y")) #formatting the dates
data$date_range_start<-as.character(data$date_range_start)
data<-data[complete.cases(data), ]
```


# Performing Regression 

Steps:
1. Construct the different models (fixed model, pooled model and Random). 
2. Test for the most appropriate model using the F-test, Hausman test, and BP test. 
3. Find the summary of the best model. 
4. Construct Interaction Plots
5. Find the confidence interval for any distance threshold using the delat method. 


## Race = None
### Creating Different models and testing if they are suitable

### Creating the models  


#### Fixed model

```{r}
fixed_model <- plm(log(visitor_count) ~covid_era+ log(dist)+covid_era:log(dist)+log(population/1000),data = data,index = c("date_range_start"), model="within")
```


#### pooled model 
```{r}
pooled_model <- plm(log(visitor_count) ~covid_era+ log(dist)+covid_era:log(dist)+log(population/1000),data = data,index = c("date_range_start"), model="pooling")
 
```


#### random model
```{r}
random_model <- plm(log(visitor_count) ~covid_era+ log(dist)+covid_era:log(dist)+log(population/1000),data = data,index = c("date_range_start"), model="random")
```


### Testing to see which model is better

#### test for fixed vs pooled_model
```{r}
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
```

#### Test for fixed vs random effects  

```{r}
phtest(fixed_model, random_model) # fixed model is better
```


#### Test for pooled vs random effects
```{r}
plmtest(pooled_model, type=c("bp"))
```



## Random model is the best so we can the fixed model results

```{r}
summary(random_model)
```
```{r}
stargazer(random_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(random_model, effect = "individual", model = "between")), 3))))
```



## Getting the interaction plots

### variable distance 

```{r}
none.random.2 <- effect('covid_era*log(dist)', random_model,xlevels=list(log(data$dist)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
none.random.2 <-as.data.frame(none.random.2)
#random.2$covid_era<-factor(random.2$covid_era,
#              levels=c("True", "False"))
none.Plot.2<-ggplot(data=none.random.2 , aes(x=log(dist), y=fit, group=covid_era))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=covid_era))+
      ylab("ln(visitation)")+
      xlab("ln(distance in km)")+
      ggtitle("Interact Plot between distance and covid era")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "COVID19 era")
none.Plot.2
```



#### getting the distance CI with Delta method
```{r}

cov_y<-vcov(random_model)[2,2]
cov_x<-vcov(random_model)[5,5]
cov_xy<-vcov(random_model)[2,5]
square_root<-sqrt(cov_y+cov_x-cov_xy)
R<-as.numeric((random_model$coefficients)[2])/as.numeric(-(random_model$coefficients)[5])
SE<-R*square_root
CI_log<-c(R-1.96*SE,R+1.96*SE)
exp(CI_log)
```


## Race = non-white

### Creating Different models and testing if they are suitable

### Creating the models  


#### Fixed model

```{r}
fixed_model <- plm(log(visitor_count) ~covid_era+ log(minorityportion)+log(dist)+covid_era:log(minorityportion)+covid_era:log(dist)+log(dist):log(minorityportion)+covid_era:log(dist):log(minorityportion)+log(population/1000),data = data,index = c("date_range_start"), model="within")
```


#### pooled model 
```{r}
pooled_model <- plm(log(visitor_count) ~covid_era+ log(minorityportion)+log(dist)+covid_era:log(minorityportion)+covid_era:log(dist)+log(dist):log(minorityportion)+covid_era:log(dist):log(minorityportion)+log(population/1000),data = data,index = c("date_range_start"),model="pooling")
 
```


#### random model
```{r}
random_model <- plm(log(visitor_count) ~covid_era+log(minorityportion)+log(dist)+covid_era:log(minorityportion)+log(minorityportion)+covid_era:log(dist)+log(dist):log(minorityportion)+covid_era:log(dist):log(minorityportion)+log(population/1000),data = data,index = c("date_range_start"), model="random")
```


### Testing to see which model is better

#### test for fixed vs pooled_model
```{r}
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
```

### Test for fixed vs random effects  
```{r}
phtest(fixed_model, random_model) # fixed model is better
```


### Test for pooled vs random effects
```{r}
plmtest(pooled_model, type=c("bp"))
```



## Random model is the best so we can the fixed model results

```{r}
summary(random_model)
```
```{r}
stargazer(random_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(random_model, effect = "individual", model = "between")), 3))))
```




## Getting the interaction plots

### variable race (non-white)

```{r}
#Our interaction
non.white.random.1 <- effect('covid_era*log(minorityportion)', random_model,xlevels=list(log(data$minorityportion)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
non.white.random.1 <-as.data.frame(non.white.random.1)
#random.2$covid_era<-factor(random.2$covid_era,
#              levels=c("True", "False"))
non.white.Plot.1<-ggplot(data=non.white.random.1, aes(x=((minorityportion)), y=fit, group=covid_era))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=covid_era))+
      ylab("ln(visitation)")+
      xlab("% of non-white")+
      ggtitle("Interact Plot between non-whites and covid era")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "COVID19 era") 
non.white.Plot.1
```

### variable distance 

```{r}
non_white.random.2 <- effect('covid_era*log(dist)', random_model,xlevels=list(log(data$dist)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
non_white.random.2 <-as.data.frame(non_white.random.2)
#random.2$covid_era<-factor(random.2$covid_era,
#              levels=c("True", "False"))
non_white.Plot.2<-ggplot(data=non_white.random.2 , aes(x=log(dist), y=fit, group=covid_era))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=covid_era))+
      ylab("ln(visitation)")+
      xlab("ln(distance in km)")+
      ggtitle("Interact Plot between distance and covid era")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "COVID19 era")
non_white.Plot.2
```


### Variable Distance and Race
```{r}
#Run the interaction 
sd.3<-sd(log(data[data$covid_era==F,]$minorityportion))
non_white.random.3 <- effect('log(minorityportion)*log(dist)', random_model,xlevels=list(log(data[data$covid_era==F,]$dist),log(data[data$covid_era==F,]$minorityportion)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
non_white.random.3<- as.data.frame(non_white.random.3)
#Check out what the "head" (first 6 rows) of your data looks like
#head(random.4)
non_white.Plot.3<-ggplot(data=non_white.random.3, aes(x=minorityportion, y=fit, group=dist))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=dist))+
      ylab("ln(visitation)")+
      xlab("% of non-whites")+
      ggtitle("COVID era = FALSE")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),legend.position = "none")+
      scale_fill_grey()+ labs(colour = "distance (m)")
non_white.Plot.3
#Plot.HandPick 
#Run the interaction 
sd.5<-sd(log(data[data$covid_era==T,]$minorityportion))
non_white.random.4 <- effect('log(minorityportion)*log(dist)', random_model,xlevels=list(log(data[data$covid_era==T,]$dist),log(data[data$covid_era==T,]$minorityportion)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
non_white.random.4<- as.data.frame(non_white.random.4)
library(ggplot2)                
non_white.Plot.4<-ggplot(data=non_white.random.4, aes(x=minorityportion, y=fit, group=dist))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=dist))+
      ylab("ln(visitation)")+
      xlab("% of non-whites")+
      ggtitle("COVID era = TRUE")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "distance (m)")
#Plot.5
non_white.threeway<-ggarrange(non_white.Plot.3, non_white.Plot.4, ncol=2,widths=c(4/9,5/9))
non_white.threeway<-annotate_figure(non_white.threeway, top = textGrob("Interact Plot between distance and percent of non-whites and COVID era"))
```


#### getting the distance CI with Delta method
```{r}

cov_y<-vcov(random_model)[6,6]
cov_x<-vcov(random_model)[9,9]
cov_xy<-vcov(random_model)[6,9]
square_root<-sqrt(cov_y+cov_x-2*cov_xy)
R<-as.numeric((random_model$coefficients)[6])/as.numeric(-(random_model$coefficients)[9])
SE<-R*square_root
CI_log<-c(R-1.96*SE,R+1.96*SE)
exp(CI_log)
```

## Race = African American

## Creating Different models and testing if they are suitable

### Creating the models  


#### Fixed model

```{r}
fixed_model <- plm(log(visitor_count) ~covid_era+ log(percent_black)+log(dist)+covid_era:log(percent_black)+covid_era:log(dist)+log(dist):log(percent_black)+covid_era:log(dist):log(percent_black)+log(population/1000),data = data,index = c("date_range_start"), model="within")
```


#### pooled model 
```{r}
pooled_model <- plm(log(visitor_count) ~covid_era+ log(percent_black)+log(dist)+covid_era:log(percent_black)+covid_era:log(dist)+log(dist):log(percent_black)+covid_era:log(dist):log(percent_black)+log(population/1000),data=data ,index = c("date_range_start"),model="pooling")
 
```


#### random model
```{r}
random_model <- plm(log(visitor_count) ~covid_era+ log(percent_black)+log(dist)+covid_era:log(percent_black)+covid_era:log(dist)+log(dist):log(percent_black)+covid_era:log(dist):log(percent_black)+log(population/1000),data=data,index = c("date_range_start"), model="random")
```


### Testing to see which model is better

#### test for fixed vs pooled_model
```{r}
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
```

#### Test for fixed vs random effects  

```{r}
phtest(random_model, fixed_model) # fixed model is better
```
#### Test for pooled vs random effects
```{r}
plmtest(pooled_model, type=c("bp"))
```

### Random Model is the best so we use random model results

```{r}
summary(random_model)
```

```{r}
stargazer(random_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(random_model, effect = "individual", model = "between")), 3))))
```



## Getting Interaction Plots

### Variable Distance
```{r}
black.random.2 <- effect('covid_era*log(dist)', random_model,xlevels=list(log(data$dist)),se=TRUE, hispanic.level=.95, typical=mean)
#Put data in data frame 
black.random.2 <-as.data.frame(black.random.2)
#random.2$covid_era<-factor(random.2$covid_era,
#              levels=c("True", "False"))
black.Plot.2<-ggplot(data=black.random.2 , aes(x=log(dist), y=fit, group=covid_era))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=covid_era))+
      ylab("ln(visitation)")+
      xlab("ln(Distance in km)")+
      ggtitle("Interact Plot between distance and covid era")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "COVID19 era")
black.Plot.2
```

### Variable Distance and Race
```{r}
black.random.4 <- effect('log(percent_black):log(dist)', random_model,xlevels=list(log(data$dist),log(data$percent_black)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
black.random.4<- as.data.frame(black.random.4)
black.Plot.4<-ggplot(data=black.random.4, aes(x=percent_black, y=fit, group=dist))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=dist))+
      ylab("ln(visitation)")+
      xlab("% of African Americans")+
      ggtitle("Interact Plot between distance and percent of African Americans")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "distance (m)")
black.Plot.4
```

## Hispanic
### Creating Different models and testing if they are suitable

#### Fixed model

```{r}
fixed_model <- plm(log(visitor_count) ~covid_era+ log(percent_hispanic)+log(dist)+covid_era:log(percent_hispanic)+covid_era:log(dist)+log(dist):log(percent_hispanic)+covid_era:log(dist):log(percent_hispanic)+log(population/1000),data = data,index = c("date_range_start"), model="within")
```


#### pooled model 
```{r}
pooled_model <- plm(log(visitor_count) ~covid_era+ log(percent_hispanic)+log(dist)+covid_era:log(percent_hispanic)+covid_era:log(dist)+log(dist):log(percent_hispanic)+covid_era:log(dist):log(percent_hispanic)+log(population/1000),data=data ,index = c("date_range_start"),model="pooling")
 
```


#### random model
```{r}
random_model <- plm(log(visitor_count) ~covid_era+ log(percent_hispanic)+log(dist)+covid_era:log(percent_hispanic)+covid_era:log(dist)+log(dist):log(percent_hispanic)+covid_era:log(dist):log(percent_hispanic)+log(population/1000),data=data,index = c("date_range_start"), model="random")
```


### Testing to see which model is better

#### test for fixed vs pooled_model
```{r}
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
```

#### Test for fixed vs random effects  

```{r}
phtest(fixed_model, random_model) # fixed model is better
```

#### Test for pooled vs random effects
```{r}
plmtest(pooled_model, type=c("bp"))
```

### Random Model is the best so we use random model results

```{r}
summary(random_model)
```


```{r}
stargazer(random_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(random_model, effect = "individual", model = "between")), 3))))
```


## Creating Interaction Plots


### Variable Distance 

```{r}
hispanic.random.2 <- effect('covid_era*log(dist)', random_model,xlevels=list(log(data$dist)),se=TRUE, hispanic.level=.95, typical=mean)
#Put data in data frame 
hispanic.random.2 <-as.data.frame(hispanic.random.2)
#random.2$covid_era<-factor(random.2$covid_era,
#              levels=c("True", "False"))
hispanic.Plot.2<-ggplot(data=hispanic.random.2 , aes(x=log(dist), y=fit, group=covid_era))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=covid_era))+
      ylab("ln(visitation)")+
      xlab("ln(distance in km)")+
      ggtitle("Interact Plot between distance and covid era")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "COVID19 era")
hispanic.Plot.2
```

### Variable Distance and race 

```{r}
hispanic.random.4 <- effect('log(percent_hispanic)*log(dist)', random_model,xlevels=list(log(data$dist),log(data$percent_hispanic)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
hispanic.random.4<- as.data.frame(hispanic.random.4)
hispanic.Plot.4<-ggplot(data=hispanic.random.4, aes(x=percent_hispanic, y=fit, group=dist))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=dist))+
      ylab("ln(visitation)")+
      xlab("% of Hispanic")+
      ggtitle("Interact Plot between distance and Percent of hispanics")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "distance (m)")
hispanic.Plot.4
```



## Race = Asian American
### Creating Different models and testing if they are suitable


#### Fixed model

```{r}
fixed_model <- plm(log(visitor_count) ~covid_era+ log(percent_asian)+log(dist)+covid_era:log(percent_asian)+covid_era:log(dist)+log(dist):log(percent_asian)+covid_era:log(dist):log(percent_asian)+log(population/1000),data = data,index = c("date_range_start"), model="within")
```


#### pooled model 
```{r}
pooled_model <- plm(log(visitor_count) ~covid_era+ log(percent_asian)+log(dist)+covid_era:log(percent_asian)+covid_era:log(dist)+log(dist):log(percent_asian)+covid_era:log(dist):log(percent_asian)+log(population/1000),data=data ,index = c("date_range_start"),model="pooling")
 
```


#### random model
```{r}
random_model <- plm(log(visitor_count) ~covid_era+ log(percent_asian)+log(dist)+covid_era:log(percent_asian)+covid_era:log(dist)+log(dist):log(percent_asian)+covid_era:log(dist):log(percent_asian)+log(population/1000),data=data,index = c("date_range_start"), model="random")
```


### Testing to see which model is better

#### test for fixed vs pooled_model
```{r}
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
```

#### Test for fixed vs random effects  

```{r}
phtest(random_model,fixed_model) # random model is better
```

####Test for pooled vs random effects
```{r}
plmtest(pooled_model, type=c("bp"))
```

#### Random model is the best so we can the fixed model results

```{r}
summary(random_model)
```

```{r}
stargazer(random_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(random_model, effect = "individual", model = "between")), 3))))
```



### Getting Interaction Plots
## Variable Distance

```{r}
asian.random.2 <- effect('covid_era*log(dist)', random_model,xlevels=list(log(data$dist)),se=TRUE, hispanic.level=.95, typical=mean)
#Put data in data frame 
asian.random.2 <-as.data.frame(asian.random.2)
#random.2$covid_era<-factor(random.2$covid_era,
#              levels=c("True", "False"))
asian.Plot.2<-ggplot(data=asian.random.2 , aes(x=log(dist), y=fit, group=covid_era))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=covid_era))+
      ylab("ln(visitation)")+
      xlab("ln(Distance in m)")+
      ggtitle("Interact Plot between distance and covid era")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "COVID19 era")
asian.Plot.2
```

## Variable Distance and Race
```{r}
asian.random.4 <- effect('log(percent_asian)*log(dist)', random_model,xlevels=list(log(data$dist),log(data$percent_asian)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
asian.random.4<- as.data.frame(asian.random.4)
                
asian.Plot.4<-ggplot(data=asian.random.4, aes(x=percent_asian, y=fit, group=dist))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=dist))+
      ylab("ln(visitation)")+
      xlab("% of Asian American")+
      ggtitle("Interact Plot between distance and percent of Asian Americans")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "distance (m)")
#Plot.5
asian.Plot.4
```







## Race = Indian American
### Creating Different models and testing if they are suitable


#### Fixed model

```{r}
fixed_model <- plm(log(visitor_count) ~covid_era+ log(percent_indian)+log(dist)+covid_era:log(percent_indian)+covid_era:log(dist)+log(dist):log(percent_indian)+covid_era:log(dist):log(percent_indian)+log(population/1000),data = data,index = c("date_range_start"), model="within")
```


#### pooled model 
```{r}
pooled_model <- plm(log(visitor_count) ~covid_era+ log(percent_indian)+log(dist)+covid_era:log(percent_indian)+covid_era:log(dist)+log(dist):log(percent_indian)+covid_era:log(dist):log(percent_indian)+log(population/1000),data=data ,index = c("date_range_start"),model="pooling")
 
```


#### random model
```{r}
random_model <- plm(log(visitor_count) ~covid_era+ log(percent_indian)+log(dist)+covid_era:log(percent_indian)+covid_era:log(dist)+log(dist):log(percent_indian)+covid_era:log(dist):log(percent_indian)+log(population/1000),data=data,index = c("date_range_start"), model="random")
```


### Testing to see which model is better

#### test for fixed vs pooled_model
```{r}
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
```

#### Test for fixed vs random effects  

```{r}
phtest(random_model,fixed_model) # random model is better
```

#### Test for pooled vs random effects
```{r}
plmtest(pooled_model, type=c("bp"))
```

### Random model is the best so we can the find results

```{r}
summary(random_model)
```


```{r}
stargazer(random_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(random_model, effect = "individual", model = "between")), 3))))
```


## Plotting Interaction Plots
### variable race 

```{r}
#Our interaction
indian.random.1 <- effect('covid_era*log(percent_indian)',random_model,xlevels=list(log(data$percent_indian)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
indian.random.1 <-as.data.frame(indian.random.1)
#random.2$covid_era<-factor(random.2$covid_era,
#              levels=c("True", "False"))
indian.Plot.1<-ggplot(data=indian.random.1, aes(x=percent_indian, y=fit, group=covid_era))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=covid_era))+
      ylab("ln(visitation)")+
      xlab("% of Native Americans")+
      ggtitle("Interact Plot between Native Americans and covid era")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "COVID19 era") 
indian.Plot.1
```

### variable distance 

```{r}
indian.random.2 <- effect('covid_era*log(dist)', random_model,xlevels=list(log(data$dist)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
indian.random.2 <-as.data.frame(indian.random.2)
#random.2$covid_era<-factor(random.2$covid_era,
#              levels=c("True", "False"))
indian.Plot.2<-ggplot(data=indian.random.2 , aes(x=log(dist), y=fit, group=covid_era))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=covid_era))+
      ylab("ln(visitation)")+
      xlab("Distance (m)")+
      ggtitle("Interact Plot between distance and covid era")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "COVID19 era")
indian.Plot.2
#Run the interaction 
sd.3<-sd(log(data[data$covid_era==F,]$percent_indian))
indian.random.3 <- effect('log(percent_indian)*log(dist)', random_model,xlevels=list(log(data[data$covid_era==F,]$dist),log(data[data$covid_era==F,]$percent_indian)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
indian.random.3<- as.data.frame(indian.random.3)
#Check out what the "head" (first 6 rows) of your data looks like
#head(random.4)
indian.Plot.3<-ggplot(data=indian.random.3, aes(x=percent_indian, y=fit, group=dist))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=dist))+
      ylab("ln(visitation)")+
      xlab("% of Native Americans")+
      ggtitle("COVID era = FALSE")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),legend.position = "none")+
      scale_fill_grey()+ labs(colour = "distance (m)")
indian.Plot.3
#Plot.HandPick 
```


### Variable Distance and Race
```{r}
#Run the interaction 
sd.5<-sd(log(data[data$covid_era==T,]$percent_indian))
indian.random.4 <- effect('log(percent_indian)*log(dist)', random_model,xlevels=list(log(data[data$covid_era==T,]$dist),log(data[data$covid_era==T,]$percent_indian)),se=TRUE, confidence.level=.95, typical=mean)
#Put data in data frame 
indian.random.4<- as.data.frame(indian.random.4)
library(ggplot2)                
Indian.Plot.4<-ggplot(data=indian.random.4, aes(x=percent_indian, y=fit, group=dist))+  
#For ylim, specify the range of your DV (in our case, 0-4)
      geom_line(size=1, aes(color=dist))+
      ylab("log(visitations)")+
      xlab("% of Indian-Americans")+
      ggtitle("COVID era = TRUE")+
      theme_bw()+ 
        theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())+
      scale_fill_grey()+ labs(colour = "distance (m)")
#Plot.5
indian.threeway<-ggarrange(indian.Plot.3, Indian.Plot.4, ncol=2,widths=c(4/9,5/9))
indian.threeway<-annotate_figure(indian.threeway, top = textGrob("Interact Plot between distance and percent of Indian-Americans and COVID era"))
```

#### getting the distance CI with Delta method
```{r}

cov_y<-vcov(random_model)[6,6]
cov_x<-vcov(random_model)[9,9]
cov_xy<-vcov(random_model)[6,9]
square_root<-sqrt(cov_y+cov_x-2*cov_xy)
R<-as.numeric((random_model$coefficients)[6])/as.numeric(-(random_model$coefficients)[9])
SE<-R*square_root
CI_log<-c(R-1.96*SE,R+1.96*SE)
exp(CI_log)
```


# Compiling the plots 

```{r}
#install.packages("gridExtra")
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
not_measured<-ggplot() +annotate("text",x = 1,y = 1,size = 8,label = "Not in model")+theme_void()
empty<-ggplot() +annotate("text",x = 1,y = 1,size = 8,label = "No significance")+theme_void()
zero<-arrangeGrob(not_measured,none.Plot.2,not_measured,
  nrow = 1,
  left = textGrob("Race = (None)\n", rot = 90, vjust = 1,gp=gpar(cex=2.5)))
first<-arrangeGrob(non.white.Plot.1,non_white.Plot.2,non_white.threeway,
  nrow = 1,
  left = textGrob("Race = Non-white\n", rot = 90, vjust = 1,gp=gpar(cex=2.5)))
second<-arrangeGrob(
  empty,black.Plot.2,black.Plot.4,
  nrow = 1,
  left = textGrob("Race = African American\n", rot = 90, vjust = 1,gp=gpar(cex=2.5)))
third<-arrangeGrob(empty,hispanic.Plot.2,hispanic.Plot.4,
  nrow = 1,
  left = textGrob("Race = Hispanic\n", rot = 90, vjust = 1,gp=gpar(cex=2.5)))
forth<-arrangeGrob(empty,asian.Plot.2,asian.Plot.4,
  nrow = 1,
  left = textGrob("Race = Asian American\n", rot = 90, vjust = 1,gp=gpar(cex=2.5)))
fifth<-arrangeGrob(indian.Plot.1,indian.Plot.2,indian.threeway,
  nrow = 1,
  left = textGrob("Race = Native American\n", rot = 90, vjust = 1,gp=gpar(cex=2.5)))
grid.arrange(zero,first,second,third,forth,fifth,nrow=6)
```
