# Reading the data and preparing it for the regression analysis. 
## Download library packages and load datasets
```{r}
library(effects)
library(cowplot)
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
library(ggpubr)
library(effects)
library(stargazer)
library(purrr)
library(plm)
library(data.table)
library(bit64)
options(scipen = 999)
library(knitr)
library(broom)
library(tseries) # for `adf.test()`
library(dynlm) #for function `dynlm()`
library(vars) # for function `VAR()`
library(nlWaldTest) # for the `nlWaldtest()` function
library(lmtest) #for `coeftest()` and `bptest()`.
library(car) #for `hccm()` robust standard errors
library(sandwich)
library(knitr) #for `kable()`
library(forecast) 
library(systemfit)
library(AER)
library(xtable)
library(jtools)
library(devtools)
library(interactions)
library(ggplot2)
library(sjPlot)
library(sjmisc)
data<-read.csv("national_park_visitation_analysis_w_mobile_phone_data/volume/data/processed/processed_model.csv")
data<-subset(data, select = c(vistor_census_block,minorityportion,median.age,dist,MEDIAN.INCOME, visitor_count, PARKNAME, date_range_start))
data<-data[complete.cases(data), ]
data$dist<-(data$dist)/1000 # Standardize distance to kilometers
```

## Remove Puerto Rico, Hawaii, Alaska, US minor Islands. 
```{r}
data$length<-floor(log10(data$vistor_census_block)) + 1
data_eleven<-data[(data$length==11),]
data_eleven$first<-as.numeric(substr(data_eleven$vistor_census_block, 1, 1))
data_twelve<-data[(data$length==12),]
data_twelve$first_second<-as.numeric(substr(data_twelve$vistor_census_block, 1, 2))
data_eleven<-data_eleven[!data_eleven$first == 2, ]
cbg_unwanted<-c(60,66,69,72,78,15)
data_twelve<-data_twelve[!data_twelve$first_second %in% cbg_unwanted,]
data_eleven<-subset(data_eleven, select=-c(length, first))
data_twelve<-subset(data_twelve, select=-c(length, first_second))
data<-rbind(data_eleven,data_twelve)


# cleaning the data
data$population_per_thousand<-(data$population)/1000
data<-subset(data, select=c(vistor_census_block,PARKNAME,covid_era,date_range_start,visitor_count,dist,population_per_thousand,percent_hispanic,percent_asian,percent_indian,percent_black,minorityportion))
DT.m1 = melt(data, id.vars = c("vistor_census_block", "PARKNAME", "covid_era","date_range_start","visitor_count"),
                measure.vars = c("dist", "population_per_thousand", "percent_hispanic","percent_asian","percent_indian","percent_black","minorityportion"))
DT.m1<-subset(DT.m1,select=-c(covid_era,vistor_census_block,PARKNAME,date_range_start))
DT.m1$variable<-as.character(DT.m1$variable)
DT.m1$variable[DT.m1$variable == "dist"] <- "distance"
DT.m1$variable[DT.m1$variable == "population_per_thousand"] <- "population/1000"
DT.m1$variable[DT.m1$variable == "percent_asian"] <- "% of Asian-Americans"
DT.m1$variable[DT.m1$variable == "percent_indian"] <- "% of Native-Americans"
DT.m1$variable[DT.m1$variable == "percent_hispanic"] <- "% of Hispanics"
DT.m1$variable[DT.m1$variable == "percent_black"] <- "% of African-Americans"
DT.m1$variable[DT.m1$variable == "minorityportion"] <- "% of non-whites"



```

Steps: 
1. Test for log-linearity
2. Test for multi-collinearity

# testing for log-linearity

## race=(none) model

```{r}
DT1<-DT.m1[!(DT.m1$variable%in% c("% of Asian-Americans","% of Native-Americans","% of Hispanics","% of African-Americans","% of non-whites")),]
ggplot(DT1, aes(log(visitor_count), log(value)))+
  geom_smooth(method="gam")+ theme_bw() + facet_wrap(~variable, nrow = 2)+xlab("ln(visitor count)")+ylab("ln(independent variable)")
```


## race=non-white model
```{r}

DT1<-DT.m1[!(DT.m1$variable%in% c("% of Asian-Americans","% of Native-Americans","% of Hispanics","% of African-Americans")),]
ggplot(DT1, aes(log(visitor_count), log(value)))+
  geom_smooth(method="gam")+ theme_bw() + facet_wrap(~variable, nrow = 2)+xlab("ln(visitor count)")+ylab("ln(independent variable)")


```

## race=african-American
```{r}

DT1<-DT.m1[!(DT.m1$variable%in% c("% of Asian-Americans","% of Native-Americans","% of Hispanics","% of non-whites")),]
ggplot(DT1, aes(log(visitor_count), log(value)))+geom_smooth(method="gam")+ theme_bw() + facet_wrap(~variable,nrow=2)+xlab("ln(visitor count)")+ylab("ln(independent variable)")


```

## race=hispanics
```{r}

DT1<-DT.m1[!(DT.m1$variable%in% c("% of Asian-Americans","% of Native-Americans","% of African-Americans","% of non-whites")),]
ggplot(DT1, aes(log(visitor_count), log(value)))+geom_smooth(method="gam")+ theme_bw() + facet_wrap(~variable, nrow=2)+xlab("ln(visitor count)")+ylab("ln(independent variable)")


```

## race=asian-american
```{r}

DT1<-DT.m1[!(DT.m1$variable%in% c("% of Native-Americans","% of African-Americans","% of non-whites","% of Hispanics")),]
ggplot(DT1, aes(log(visitor_count), log(value)))+
  geom_smooth(method="gam")+ theme_bw() + facet_wrap(~variable,nrow=2)+xlab("ln(visitor count)")+ylab("ln(independent variable)")



```

## race=native-American
```{r}
DT1<-DT.m1[!(DT.m1$variable%in% c("% of Asian-Americans","% of African-Americans","% of non-whites","% of Hispanics")),]
ggplot(DT1, aes(log(visitor_count), log(value)))+
  geom_smooth(method="gam")+ theme_bw() + facet_wrap(~variable, nrow=2)+xlab("ln(visitor count)")+ylab("ln(independent variable)")
```


# Testing for multi-collinearity

## race=(none)

```{r}
(vif(lm(log(visitor_count) ~covid_era+log(dist)+covid_era:log(dist)+covid_era:log(dist):log(minorityportion)+log(population/1000)+(date_range_start), data=data)))
```


## race=non-white

```{r}
vif(lm(log(visitor_count) ~covid_era+ log(minorityportion)+log(dist)+covid_era:log(minorityportion)+covid_era:log(dist)+log(dist):log(minorityportion)+covid_era:log(dist):log(minorityportion)+log(population/1000)+(date_range_start), data=data))
```


## race=african-american

```{r}
vif(lm(log(visitor_count) ~covid_era+ log(percent_black)+log(dist)+covid_era:log(percent_black)+covid_era:log(dist)+log(dist):log(percent_black)+covid_era:log(dist):log(percent_black)+log(population/1000)+(date_range_start),data = data))
```


## race=hispanics
```{r}
vif(lm(log(visitor_count) ~covid_era+ log(percent_hispanic)+log(dist)+covid_era:log(percent_hispanic)+covid_era:log(dist)+log(dist):log(percent_hispanic)+covid_era:log(dist):log(percent_hispanic)+log(population/1000)+date_range_start,data=data))
```


## race=asian_americans
```{r}
vif(lm(log(visitor_count) ~covid_era+ log(percent_asian)+log(dist)+covid_era:log(percent_asian)+covid_era:log(dist)+log(dist):log(percent_asian)+covid_era:log(dist):log(percent_asian)+log(population/1000)+(date_range_start),data = data))
```


## race=native-american
```{r}
vif(lm(log(visitor_count) ~covid_era+ log(percent_indian)+log(dist)+covid_era:log(percent_indian)+covid_era:log(dist)+log(dist):log(percent_indian)+covid_era:log(dist):log(percent_indian)+log(population/1000)+(date_range_start),data = data))
```


