# Reading the data and preparing it for the regression analysis. 
## Download library packages and load datasets
```{r}
library(effects)
library(cowplot)
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
library(ggpubr)
library(effects)
library(stargazer)
library(purrr)
library(plm)
library(data.table)
library(bit64)
options(scipen = 999)
library(knitr)
library(broom)
library(tseries) # for `adf.test()`
library(dynlm) #for function `dynlm()`
library(vars) # for function `VAR()`
library(nlWaldTest) # for the `nlWaldtest()` function
library(lmtest) #for `coeftest()` and `bptest()`.
library(car) #for `hccm()` robust standard errors
library(sandwich)
library(knitr) #for `kable()`
library(forecast) 
library(systemfit)
library(AER)
library(xtable)
library(jtools)
library(devtools)
library(interactions)
library(ggplot2)
library(sjPlot)
library(sjmisc)
data<-read.csv("national_park_visitation_analysis_w_mobile_phone_data/volume/data/processed/processed_model.csv")
data<-subset(data, select = c(vistor_census_block,minorityportion,median.age,dist,MEDIAN.INCOME, visitor_count, PARKNAME, date_range_start))
data<-data[complete.cases(data), ]
data$dist<-(data$dist)/1000 # Standardize distance to kilometers
```

## Remove Puerto Rico, Hawaii, Alaska, US minor Islands. 
```{r}
data$length<-floor(log10(data$vistor_census_block)) + 1
data_eleven<-data[(data$length==11),]
data_eleven$first<-as.numeric(substr(data_eleven$vistor_census_block, 1, 1))
data_twelve<-data[(data$length==12),]
data_twelve$first_second<-as.numeric(substr(data_twelve$vistor_census_block, 1, 2))
data_eleven<-data_eleven[!data_eleven$first == 2, ]
cbg_unwanted<-c(60,66,69,72,78,15)
data_twelve<-data_twelve[!data_twelve$first_second %in% cbg_unwanted,]
data_eleven<-subset(data_eleven, select=-c(length, first))
data_twelve<-subset(data_twelve, select=-c(length, first_second))
data<-rbind(data_eleven,data_twelve)
```


## Prepare the model for Regression. 
```{r}
data[data==0] = 0.0000000000000000000001 # Beacause natural log could not take 0's
# Classify COVID vs non-COVID era
data$date_range_start<-as.Date(data$date_range_start,"%Y-%m-%d") 
data_non<-data[(data$date_range_start<"2020-03-01"),]
data_covid<-data[(data$date_range_start>="2020-03-01"),]
data_covid$covid_era<-TRUE
data_non$covid_era<-FALSE
data<-rbind(data_covid, data_non)
data<-data[complete.cases(data), ]
data$date_range_start<-month(as.POSIXlt(data$date_range_start, format="%d/%m/%Y")) #formatting the dates
data$date_range_start<-as.character(data$date_range_start)
data<-data[complete.cases(data), ]

# read the park area csv file

area<-read.csv("national_park_visitation_analysis_w_mobile_phone_data/volume/data/interim/area_of_parks/area_of_parks.csv")
data<-merge(data,area,by.y="PARKNAME",by.x="PARKNAME",all.x=T)
```




# Considering Area as the denominator of the gravity model. 

## race=(none) model

```{r}

fixed_model <- plm(log(visitor_count) ~covid_era+ log(area_sqkm)+covid_era:log(area_sqkm)+log(population/1000),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count) ~covid_era+ log(area_sqkm)+covid_era:log(area_sqkm)+log(population/1000),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count) ~covid_era+ log(area_sqkm)+covid_era:log(area_sqkm)+log(population/1000),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
## Test for fixed vs random effects  
phtest(fixed_model, random_model) # fixed model is better
## Test for pooled vs random effects
plmtest(pooled_model, type=c("bp"))

stargazer(fixed_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(fixed_model, effect = "individual", model = "between")), 3))))
```


## race=non-white model

```{r}
fixed_model <- plm(log(visitor_count) ~covid_era+log(minorityportion)+log(area_sqkm)+covid_era:log(minorityportion)+log(minorityportion)+covid_era:log(area_sqkm)+log(area_sqkm):log(minorityportion)+covid_era:log(area_sqkm):log(minorityportion)+log(population/1000),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count) ~covid_era+log(minorityportion)+log(area_sqkm)+covid_era:log(minorityportion)+log(minorityportion)+covid_era:log(area_sqkm)+log(area_sqkm):log(minorityportion)+covid_era:log(area_sqkm):log(minorityportion)+log(population/1000),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count) ~covid_era+log(minorityportion)+log(area_sqkm)+covid_era:log(minorityportion)+log(minorityportion)+covid_era:log(area_sqkm)+log(area_sqkm):log(minorityportion)+covid_era:log(area_sqkm):log(minorityportion)+log(population/1000),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
## Test for fixed vs random effects  
phtest(fixed_model, random_model) # fixed model is better
## Test for pooled vs random effects
plmtest(pooled_model, type=c("bp"))

stargazer(fixed_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(fixed_model, effect = "individual", model = "between")), 3))))
```

## race=african-american model

```{r}

fixed_model <- plm(log(visitor_count) ~covid_era+log(percent_black)+log(area_sqkm)+covid_era:log(percent_black)+log(percent_black)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_black)+covid_era:log(area_sqkm):log(percent_black)+log(population/1000),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count) ~covid_era+log(percent_black)+log(area_sqkm)+covid_era:log(percent_black)+log(percent_black)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_black)+covid_era:log(area_sqkm):log(percent_black)+log(population/1000),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count) ~covid_era+log(percent_black)+log(area_sqkm)+covid_era:log(percent_black)+log(percent_black)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_black)+covid_era:log(area_sqkm):log(percent_black)+log(population/1000),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
## Test for fixed vs random effects  
phtest(fixed_model, random_model) # fixed model is better
## Test for pooled vs random effects
plmtest(pooled_model, type=c("bp"))

stargazer(fixed_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(fixed_model, effect = "individual", model = "between")), 3))))
```

### race=hispanic model

```{r}
# race=hispanic
fixed_model <- plm(log(visitor_count) ~covid_era+log(percent_hispanic)+log(area_sqkm)+covid_era:log(percent_hispanic)+log(percent_hispanic)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_hispanic)+covid_era:log(area_sqkm):log(percent_hispanic)+log(population/1000),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count) ~covid_era+log(percent_hispanic)+log(area_sqkm)+covid_era:log(percent_hispanic)+log(percent_hispanic)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_hispanic)+covid_era:log(area_sqkm):log(percent_hispanic)+log(population/1000),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count) ~covid_era+log(percent_hispanic)+log(area_sqkm)+covid_era:log(percent_hispanic)+log(percent_hispanic)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_hispanic)+covid_era:log(area_sqkm):log(percent_hispanic)+log(population/1000),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
## Test for fixed vs random effects  
phtest(fixed_model, random_model) # fixed model is better
## Test for pooled vs random effects
plmtest(pooled_model, type=c("bp"))

stargazer(fixed_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(fixed_model, effect = "individual", model = "between")), 3))))
```


### race=asian model

```{r}

fixed_model <- plm(log(visitor_count) ~covid_era+log(percent_asian)+log(area_sqkm)+covid_era:log(percent_asian)+log(percent_asian)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_asian)+covid_era:log(area_sqkm):log(percent_asian)+log(population/1000),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count) ~covid_era+log(percent_asian)+log(area_sqkm)+covid_era:log(percent_asian)+log(percent_asian)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_asian)+covid_era:log(area_sqkm):log(percent_asian)+log(population/1000),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count) ~covid_era+log(percent_asian)+log(area_sqkm)+covid_era:log(percent_asian)+log(percent_asian)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_asian)+covid_era:log(area_sqkm):log(percent_asian)+log(population/1000),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
## Test for fixed vs random effects  
phtest(fixed_model, random_model) # fixed model is better
## Test for pooled vs random effects
plmtest(pooled_model, type=c("bp"))

stargazer(fixed_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(fixed_model, effect = "individual", model = "between")), 3))))

```


### race=Native American model


```{r}

fixed_model <- plm(log(visitor_count) ~covid_era+log(percent_indian)+log(area_sqkm)+covid_era:log(percent_indian)+log(percent_indian)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_indian)+covid_era:log(area_sqkm):log(percent_indian)+log(population/1000),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count) ~covid_era+log(percent_indian)+log(area_sqkm)+covid_era:log(percent_indian)+log(percent_indian)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_indian)+covid_era:log(area_sqkm):log(percent_indian)+log(population/1000),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count) ~covid_era+log(percent_indian)+log(area_sqkm)+covid_era:log(percent_indian)+log(percent_indian)+covid_era:log(area_sqkm)+log(area_sqkm):log(percent_indian)+covid_era:log(area_sqkm):log(percent_indian)+log(population/1000),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) # REJECT POOLED MODEL
## Test for fixed vs random effects  
phtest(fixed_model, random_model) # fixed model is better
## Test for pooled vs random effects
plmtest(pooled_model, type=c("bp"))

stargazer(fixed_model, type = "text",add.lines=list(c("Between R2",round(r.squared(update(fixed_model, effect = "individual", model = "between")), 3))))
```

Conclusion: the $R^2$ values are too low - area is a very poor indicator of park visitation trends and changes across socio-economic variables due to COVID-19. 

# Using income as part of our variables


```{r}
# using income alone 
vif(lm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000)+date_range_start,data=data))
fixed_model <- plm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) 
phtest(fixed_model, random_model)
plmtest(pooled_model, type=c("bp"))
```



Conclusion: While the F, Hausman, and LM-Test validate the use of the random-effects gravity model, the high GVIF^(1/(2*Df)) scores suggest high multi-collinearity amongst the independent variables. 

# Using income together with race. 

```{r}

# using income with race 
vif(lm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000)+log(minorityportion)+log(minorityportion):covid_era+log(minorityportion):log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(minorityportion):covid_era+date_range_start,data=data))
fixed_model <- plm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000)+log(minorityportion)+log(minorityportion):covid_era+log(minorityportion):log(MEDIAN.INCOME),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000)+log(minorityportion)+log(minorityportion):covid_era+log(minorityportion):log(MEDIAN.INCOME),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000)+log(minorityportion)+log(minorityportion):covid_era+log(minorityportion):log(MEDIAN.INCOME),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) 
phtest(fixed_model, random_model)
plmtest(pooled_model, type=c("bp"))


vif(lm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000)+log(minorityportion)+log(minorityportion):covid_era+log(minorityportion):log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(minorityportion):covid_era+date_range_start,data=data))
fixed_model <- plm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000)+log(minorityportion)+log(minorityportion):covid_era+log(minorityportion):log(MEDIAN.INCOME),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000)+log(minorityportion)+log(minorityportion):covid_era+log(minorityportion):log(MEDIAN.INCOME),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count)~covid_era+log(dist)+log(MEDIAN.INCOME)+covid_era:log(dist)+covid_era:log(MEDIAN.INCOME)+log(MEDIAN.INCOME):log(dist)+log(population/1000)+log(minorityportion)+log(minorityportion):covid_era+log(minorityportion):log(MEDIAN.INCOME),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) 
phtest(fixed_model, random_model)
plmtest(pooled_model, type=c("bp"))
```

Conclusion: The F, Hausman, and LM-Test scores suggest that the random-effects
gravity model may not be suited for this analysis. The GVIF^(1/(2*Df)) scores are concerningly high, suggesting potential multi-collinearity. 


# Using age as a socio-economic variable. 

```{r}
# age
vif(lm(log(visitor_count)~covid_era+log(dist)+log(median.age)+covid_era:log(dist)+covid_era:log(median.age)+log(median.age):log(dist)+log(population/1000)+date_range_start,data=data))
fixed_model <- plm(log(visitor_count)~covid_era+log(dist)+log(median.age)+covid_era:log(dist)+covid_era:log(median.age)+log(median.age):log(dist)+log(population/1000),data = data,index = c("date_range_start"), model="within")
pooled_model <- plm(log(visitor_count)~covid_era+log(dist)+log(median.age)+covid_era:log(dist)+covid_era:log(median.age)+log(median.age):log(dist)+log(population/1000),data = data,index = c("date_range_start"), model="pooling")
random_model <- plm(log(visitor_count)~covid_era+log(dist)+log(median.age)+covid_era:log(dist)+covid_era:log(median.age)+log(median.age):log(dist)+log(population/1000),data = data,index = c("date_range_start"), model="random")
pFtest(fixed_model, pooled_model) 
phtest(fixed_model, random_model)
plmtest(pooled_model, type=c("bp"))
```

Conclusions: The F, Hausman, and LM-Test scores suggest that the random-effects gravity model may not be suited for this analysis. While our GVIF^(1/(2*Df)) scores are lower than that of the median income analysis, it is still concerningly high, suggesting potential multi-collinearity. 
